Distributional State Aggregation

### 2020-07-12 minutia/paper/paper.tex
minutia comprehensive clear up commit

    \begin{abstract}
        We present a state aggregation algorithm and a learning algorithm based on the former to solve a stochastic
        problem.
        The presented aggregation algorithm uses range of collected samples to provide the proper aggregation
        \textit{buckets}.
        Our approach is a batch learning by which we detect the \textit{splitting policy} using inter-quartile range
        of data for each feature.
        We then show the amount of robustness we can achieve as a guarantee of performance in presence of those
        aggregation policies.
    \end{abstract}

@@

    \section{Markov Decision Processes}
    Reinforcement learning problems can be formulated using a Markov Decision Processes (MDP)
    framework\cite{Puterman1994, Bertsekas}.
    MDPs facilitate handling sequential decision-making under uncertainty.
    Discrete discounted reward criterion is the center of focus for ease of exposition in this paper.
    For an environment and a decision maker, state space $S$ and action space $A$ are defined, respectively.
    The transition probabilities $T$ describe how likely is the next state $s'$ by taking a specific action $a$ by
    the agent in a certain state $s$ which will receive $r$ as reward.
    For a taken action $a_i$ in the state $s_i$, the decision maker will be ended up in state $s_{i+1}$ by the
    transition probabilities $P : S \times A \times S \rightarrow [0, 1]$ and wil receive reward $r_{i+1}$ from the
    rewards $R : S \times A \rightarrow \mathbb{R}$: \\
    \begin{equation}
        s_{i+1} = T(s_{i+1}|s_i, a_i)
    \end{equation}

@@

    \section{Future Works}
    We developed the presented approach with having reproducibility in mind.
    It could be served as a launching pad for the future contributors who want to surf this newly emerged field deeper.
    Future ideas to pursue is a generative model to be able to generate adversaries from a network.

>>>>

    \begin{abstract}
        Real world problems often incur large scale state spaces needing sizable amount of computation to process.
        State aggregation as an analytically-transparent mean approximates and yields lower-dimension state spaces.
%        We present a state aggregation algorithm and a learning algorithm based on the former to solve a stochastic
%        problem.
        We present a state aggregation algorithm method in Markov decision processes (MDP) inspired by histograms.
        Our approach explores a \textit{splitting policy} in direct relationship with inter-quartile range
        of collected samples.
        We then accompanied an experiment by which we show the practical promises of the approach to achieve superior
        results.
    \end{abstract}

@@

    \section{Markov Decision Processes}
    Reinforcement learning problems can be formulated using a Markov Decision Processes (MDP)
    framework\cite{Puterman1994,Sutton1998}.
    MDPs facilitate handling sequential decision-making under uncertainty.
    Discrete discounted reward criterion is the center of focus for ease of exposition in this paper.
    For an environment and a decision maker, state space $S$ and action space $A$ are defined, respectively.
    The transition probabilities $T$ describe how likely is the next state $s'$ by taking a specific action $a$ by
    the agent in a certain state $s$ which will receive $r$ as reward.
    For a taken action $a_i$ in the state $s_i$, the decision maker will be ended up in state $s_{i+1}$ by the
    transition probabilities $P : S \times A \times S \rightarrow [0, 1]$ and wil receive reward $r_{i+1}$ from the
    rewards $R : S \times A \rightarrow \mathbb{R}$: \\
    \begin{equation}
        s_{i+1} = T(s_{i+1}|s_i, a_i)
    \end{equation}

@@

    \subsection{Machine Replacement}
    This domain as a \textit{non-episodic} (continuous) task maintains a set of machines.
    The goal is to find a policy to incur the least repair needed.
    incure
    \section{Future Works}
    We developed the presented approach with having reproducibility in mind.
    It could be served as a launching pad for the future contributors who want to surf this newly emerged field deeper.
    Future ideas to pursue is a generative model to be able to generate adversaries from a network.
